Secure Composition of SPECTRE Variants

### 2023-11-01 prisc-spectre/prisc.tex
nit

Some programming languages of today enjoy strong security guarantees, such as the memory-safety guarantees given by the semantic analysis pass of a compiler for the Rust programming lanugage.
While programmers may expect that these guarantees hold even after translating their program to the target programming language, it has been shown that this expectation is false in the general case~\MK{cit constant time examples}.
Even correct compilers do not provide satisfactory guarantees and one has to resort to secure compilers~\cite{abate19,abate20,patrignani21} which preserve property satisfaction even when the compiled program is linked with arbitrary target-level code.

Compilers that give these strong security guarantees usually instrument the code with mitigation mechanisms, such as bounds checks for (spatial) memory safety.
While such source-code instrumentations can be done in a local manner, i.e., there is one compilation pass that does just this, a compiler typically consists of several compilation passes, e.g., translating to continuation-passing-style or performing optimisations, like loop unrolling or vectorisation. 
From a software engineering perspective, these passes are tackled in an individual manner and there have been efforts to make compiler correctness proofs modular as well. 
A recent line of work~\cite{kruse22,kruse23,abate21} demonstrates what is necessary for secure compilers to enjoy this modularity, effectively enabling a divide-and-conquer approach to the engineering of secure compilers.

@@

\section{Conclusion}

This short paper sketched a real-world application of the compositionality framework for secure compilers as presented in earlier work~\cite{abate21,kruse22,kruse23}. 
While few source-code transformations have been formally proven secure, it is nonetheless interesting to investigate their compatiblity relationships with other transformations on a semantic level, pretending the passes have been proven secure.
Future work considers more source-code instrumentations, not only on just speculation. 
Most interestingly, the authors would like to investigate the compatiblity of common compiler optimisations.

>>>>

Some modern programming languages enjoy strong security guarantees, for example the Rust programming languages has memory safety guarantees given by its compiler performing a semantic analysis pass.
While programmers may expect that these guarantees hold even after translating their program to the target programming language, it has been shown that this expectation is false in the general case~\MK{cit constant time examples}.
Even correct compilers do not provide satisfactory guarantees and thus one has to resort to secure compilers~\cite{abate19,abate20,patrignani21} which preserve property satisfaction even when the compiled program is linked with arbitrary target-level code.

Compilers that give these strong security guarantees usually instrument the code with mitigation mechanisms, for example they insert bounds checks for (spatial) memory safety.
While such source-code instrumentations can be done in a local manner, i.e., there is one compilation pass that does just this, a compiler typically consists of several compilation passes, e.g., translating to continuation-passing-style or performing optimisations like loop unrolling. 
From a software engineering perspective, these passes are tackled in an individual manner, so there have been efforts to make compiler correctness proofs modular. 
Recent work~\cite{kruse22,kruse23,abate21} demonstrates what is necessary for secure compilers to enjoy this modularity too, effectively enabling a divide-and-conquer approach to the engineering of secure compilers.

@@

% \section{Conclusion}

% This short paper sketched a real-world application of the compositionality framework for secure compilers as presented in earlier work~\cite{abate21,kruse22,kruse23}. 
% While few source-code transformations have been formally proven secure, it is nonetheless interesting to investigate their compatiblity relationships with other transformations on a semantic level, pretending the passes have been proven secure.
% Future work considers more source-code instrumentations, not only on just speculation. 
% Most interestingly, the authors would like to investigate the compatiblity of common compiler optimisations.
